Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-16 paper/main.tex
O_A to O_H

As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindexpull$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindexpull$ between a total space over graphics $\dtotalpull$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindexpull$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
  \vindexpullc: \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\rightarrow} \cgamma{\gbasec}{\dtotalpullc}
\end{equation}
to generate a set of equivalent sections over the graphic space $\Gamma(\gbase, \dtotalpull)$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\dtotalpullc}: \mathcal{\gbasec}^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\dtotalpullc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\dtotalpullc}: \mathcal{\gbasec}^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

@@

The set of sets of sections $\{\Gamma(\opensetg, \gtotal)\}\vert_{{\opensetg \in gbase}}$ is subcategory of \textbf{Set}; therefore the full space of graphics is a sheaf $\sheaf_{\gtotal}$

\subsubsection{Data to Graphic}
Following from \autoref{eq:artist:data_pullback_sheaf} and \autoref{eq:artist:artist_sheaf},  we propose that the artist function $\vartist$ is a natural transformation
\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalpullc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalpullc) \textcolor{artist}{\rightarrow} \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set. As defined in \autoref{eq:related-work:equivariance:natural-transform}, the artist is a natural transformation. Following from \autoref{eq:related-work:equivariance:natural_transform_commute}, the artist specifies that there are compatible inclusion maps in the data and graphic spaces

\begin{equation}
  \begin{tikzcd}
    \cgamma{\opensetgc_1}{\dtotalpullc} \arrow[dd, "\iota^*"', hook, color=set] \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] &  & \opensetgc_1 \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] \arrow[rr, "\sheafc_{\vartistc}"', color=sheaf] &  & \cgamma{\opensetgc_1}{\gtotalc} \arrow[dd, "\iota^*", hook', color=set] \\
    {} \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist]                            &  & \opensetgc_2 \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] \arrow[rr, "\sheafc_{\vartistc}", color=sheaf] \arrow[uu, "\iota" description, hook, color=base] &  & \cgamma{\opensetgc_2}{\gtotalc}                             
    \end{tikzcd}
\end{equation}
Given that $\opensetg \subseteqq \gbasec$, \autoref{eq:artist:inclusion_morphisms} can be generalized to sections over $\gbase$. This fact can be combined with \autoref{eq:artist:data_gamma_pullback} to describe the path from data sections over data space to graphic sections over graphic space
\begin{equation}
  \label{eq:artist:gamma_map}
  \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindexc^*}} \cgamma{\gbasec}{\dtotalpullc} \textcolor{artist}{\xrightarrow{\vartist}} \cgamma{\gbasec}{\gtotalc}
\end{equation}

which means that the artist can be pulled back through $\vindex^*$\footnote{Definition 3.68 in Seven Sketches in Compositionality by Fong and Spivak}
\begin{equation}
  \begin{tikzcd}
    & & {} \arrow[dd, "\vartistc" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[r, "\vindexc^*", color=artist] & \mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\dtotalpullc}", bend left, color=sheaf] \arrow[rr, "\sheaf_{\vartistc}"', bend right, color=sheaf] &                                                    & \setc \\
    &                                                                                                                                                         & {}                                                 &      
\end{tikzcd}
\end{equation}
such that the artist can be constructed over data space 
\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc_{\vindexc^*}" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em,, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexpullc} \circ\vindexc^* = \sheafc_{\dtotalc}", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}"', bend right, color=sheaf] &                                                                 & \setc \\
    & {}                                                              &      
\end{tikzcd}
\end{equation}

@@

>>>>

As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindexpull$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindexpull$ between a total space over graphics $\dtotalpull$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindexpull$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
  \vindexpullc: \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\rightarrow} \cgamma{\gbasec}{\dtotalpullc}
\end{equation}
to generate a set of equivalent sections over the graphic space $\Gamma(\gbase, \dtotalpull)$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\dtotalpullc}: \opensetgc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetgc}{\dtotalpullc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\dtotalpullc}: \mathcal{\gbasec}^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

@@

The set of sets of sections $\{\Gamma(\opensetg, \gtotal)\}\vert_{{\opensetg \in gbase}}$ is subcategory of \textbf{Set}; therefore the full space of graphics is a sheaf 
\begin{equation}
  \label{eq:artist:graphic_sheaf_gamma}
  \sheafc_{\gtotalc}: \opensetgc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetgc}{\gtotalc}
\end{equation}
which means it is 
\begin{equation}
  \label{eq:artist:graphic_sheaf_set}
  \sheafc_{\gtotalc}: \gbasec^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

\subsubsection{Data to Graphic}
Following from \autoref{eq:artist:data_pullback_sheaf} and \autoref{eq:artist:artist_sheaf},  we propose that the artist function $\vartist$ is a natural transformation of sheaf functors 
\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\dtotalpullc}", bend left, color=sheaf] \arrow[rr, "\sheafc_{\gtotalc}"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set. As defined in \autoref{eq:related-work:equivariance:natural-transform}, the artist is a natural transformation. Following from \autoref{eq:related-work:equivariance:natural_transform_commute}, the artist specifies that there are compatible inclusion maps in the data and graphic spaces

\begin{equation}
  \begin{tikzcd}
    \cgamma{\opensetgc_1}{\dtotalpullc} \arrow[dd, "\iota^*"', hook, color=set] \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] &  & \opensetgc_1 \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf] &  & \cgamma{\opensetgc_1}{\gtotalc} \arrow[dd, "\iota^*", hook', color=set] \\
    {} \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist]                            &  & \opensetgc_2 \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf] \arrow[uu, "\iota" description, hook, color=base] &  & \cgamma{\opensetgc_2}{\gtotalc}                             
    \end{tikzcd}
\end{equation}
Given that $\opensetg \subseteqq \gbasec$, \autoref{eq:artist:inclusion_morphisms} can be generalized to sections over $\gbase$. This fact can be combined with \autoref{eq:artist:data_gamma_pullback} to describe the path from data sections over data space to graphic sections over graphic space
\begin{equation}
  \label{eq:artist:gamma_map}
  \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindexc^*}} \cgamma{\gbasec}{\dtotalpullc} \textcolor{artist}{\xrightarrow{\vartist}} \cgamma{\gbasec}{\gtotalc}
\end{equation}

which means that the artist can be pulled back through $\vindex^*$\footnote{Definition 3.68 in Seven Sketches in Compositionality by Fong and Spivak}
\begin{equation}
  \begin{tikzcd}
    & & {} \arrow[dd, "\vartistc" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[r, "\vindexc^*", color=artist] & \mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\dtotalpullc}", bend left, color=sheaf] \arrow[rr, "\sheaf_{\gtotalc}"', bend right, color=sheaf] &                                                    & \setc \\
    &                                                                                                                                                         & {}                                                 &      
\end{tikzcd}
\end{equation}
such that the artist can be constructed over data space 
\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc_{\vindexc^*}" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em,, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\dtotalpullc} \circ\vindexpullc = \sheafc_{\dtotalc}", bend left, color=sheaf] \arrow[rr, "\sheafc_{\gtotalc}"', bend right, color=sheaf] &                                                                 & \setc \\
    & {}                                                              &      
\end{tikzcd}
\end{equation}

@@

\subsubsection{Equivariant Artist}
